The Galaxy Cluster Merger Catalog: An Online Repository of Mock Observations from Simulated Galaxy Cluster Mergers

### 2016-09-14 paper/ms.tex
More stuff related to notebook link
Updating the epoch page info for notebook stuff

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\textwidth]{epoch_page.png}
\caption{An example ``epoch page''. Links are provided to similar simulations with different physics at the same epoch at the top of the page. For each data type, figures of some of the fields are shown and links to download the data or display in JS9 are provided. This particular page is linked at \url{http://gcmc.hub.yt/virgo/novisc/0046/index.html}.}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\textwidth]{epoch_page2.png}
\caption{The bottom of an ``epoch page'', showing the simulated X-ray event file and the JS9 interface with a projection file loaded, and a circular region selected. This particular page is linked at \url{http://gcmc.hub.yt/virgo/novisc/0046/index.html}.}
\end{center}
\end{figure*}

@@

Each epoch page also contains a JS9 application for opening the various FITS files associated with that particular epoch. A drop-down menu is provided for navigating between the various fields in each FITS file.

>>>>

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\textwidth]{epoch_page.png}
\caption{An example ``epoch page''. Links are provided to similar simulations with different physics at the same epoch at the top of the page. For each data type, figures of some of the fields are shown and links to download the data or display in JS9 are provided. This particular page is linked at \url{http://gcmc.hub.yt/virgo/novisc/0046.html}.}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\textwidth]{epoch_page2.png}
\caption{The bottom of an ``epoch page'', showing the simulated X-ray event file, the link to the Jupyter notebook directions, and the JS9 interface with a projection file loaded, and a circular region selected. This particular page is linked at \url{http://gcmc.hub.yt/virgo/novisc/0046.html}.}
\end{center}
\end{figure*}

@@

A link is provided on each epoch page to the location of the files on the \code{yt Hub}, so that one may start Jupyter notebooks with access to the data. Each epoch page also contains a JS9 application for opening the various FITS files associated with that particular epoch. A drop-down menu is provided for navigating between the various fields in each FITS file.
